### 2025-05-23 manuscript.tex
minor changes

	\section*{Acknowledgements}

	The first author (V. Kamchoom) would like to thank the grant under Climate Change and Climate Variability Research in Monsoon Asia (CMON3) from National Research Council of Thailand (NRCT) and the National Natural Science Foundation of China (NSFC). The second author (A. Garg) thanks the grant XXX provided by XXX.

>>>>

	\section*{Acknowledgments}

	The first author (V. Kamchoom) would like to thank the grant under Climate Change and Climate Variability Research in Monsoon Asia (CMONA) from National Research Council of Thailand (NRCT) and the National Natural Science Foundation of China (NSFC). The second author (A. Garg) thanks the grant XXX provided by XXX.
